\textsl{Position:} Is machine learning good or bad for the natural sciences?

### 2024-05-28 paper/main.tex
Oh the horror. Finally met all requirements of ICML. Camera ready version.

\vskip 0.3in
] % For the arXiv version, move this square bracket below the abstract

\printAffiliationsAndNotice{}
\begin{abstract}
  Machine learning (ML) methods are having a huge impact across all of the sciences.
  However, ML has a strong ontology---in which only the data exist---and a strong epistemology---in which a model is considered good if it performs well on held-out training data.
  These philosophies are in strong conflict with both standard practices and key philosophies in the natural sciences.
  Here, we identify some locations for ML in the natural sciences at which the ontology and epistemology are valuable.
  For example, when an expressive machine learning model is used in a causal inference to represent the effects of confounders, such as foregrounds, backgrounds, or instrument calibration parameters, the model capacity and loose philosophy of ML can make the results more trustworthy.
  We also show that there are contexts in which the introduction of ML introduces strong, unwanted statistical biases.
  For one, when ML models are used to emulate physical (or first-principles) simulations, they introduce strong confirmation biases.
  For another, when expressive regressions are used to label datasets, those labels cannot be used in downstream joint or ensemble analyses without taking on uncontrolled biases.
  The question in the title is being asked of all of the natural sciences; that is, we are calling on the scientific communities to take a step back and consider the role and value of ML in their fields; the (partial) answers we give here come from the particular perspective of physics.
\end{abstract}

@@

We are both ML \emph{skeptics} and ML \emph{practitioners}.
We are writing this for an audience that is either developing an ML method for science applications or else bringing ML into a scientific domain.
The main points of this \documentname{} are \textsl{(1)}~that ML has places where it is very valuable in the contemporary practice of science, and \textsl{(2)}~that it also has places where it will create problems for science.
That said, we can't definitively answer the question in the title of this \documentname{} for all natural-science domains.
This paper is a call to natural-science communities to think about it, and answer it for themselves.
From the perspective of the physical sciences, our answer is ``Both.''

>>>>

\vskip 0.3in
] % For the arXiv version, comment out this square bracket

\printAffiliationsAndNotice{}
\begin{abstract}
  Machine learning (ML) methods are having a huge impact across all of the sciences.
  However, ML has a strong ontology---in which only the data exist---and a strong epistemology---in which a model is considered good if it performs well on held-out training data.
  These philosophies are in strong conflict with both standard practices and key philosophies in the natural sciences.
  Here, we identify some locations for ML in the natural sciences at which the ontology and epistemology are valuable.
  For example, when an expressive machine learning model is used in a causal inference to represent the effects of confounders, such as foregrounds, backgrounds, or instrument calibration parameters, the model capacity and loose philosophy of ML can make the results more trustworthy.
  We also show that there are contexts in which the introduction of ML introduces strong, unwanted statistical biases.
  For one, when ML models are used to emulate physical (or first-principles) simulations, they introduce strong confirmation biases.
  For another, when expressive regressions are used to label datasets, those labels cannot be used in downstream joint or ensemble analyses without taking on uncontrolled biases.
  The question in the title is being asked of all of the natural sciences; that is, we are calling on the scientific communities to take a step back and consider the role and value of ML in their fields; the (partial) answers we give here come from the particular perspective of physics.
\end{abstract}
% ] % For the arXiv version, uncomment this square bracket

@@

We are both ML \emph{skeptics} and ML \emph{practitioners}.
We are writing this for an audience that is either developing an ML method for science applications or else bringing ML into a scientific domain.
\textbf{
The main points of this \documentname{} are \textsl{(1)}~that ML has places at which it is very valuable in the contemporary practice of science, \textsl{(2)}~that ML also has places at which it will create problems for science, and \textsl{(3)}~currently it is not obvious what is the epistemic role of ML within the broader goals of the natural sciences.
%That said, we can't definitively answer the question in the title of this \documentname{} for all natural-science domains.
This paper is a call to natural-science communities to think about it, and answer the question in the title for themselves.}
From the perspective of the physical sciences, our answer is ``Both.''
